SMT-Boosted Security Types for Low-Level MPC

### 2025-11-14 toplas26/examples.tex
checkpoint

We add coercions and typing assertions to the $\ttt{secopen}$ function
to specify properties of secure openings. After noninteractively
summing a wire value $\ttt{x}$ and a random Beaver triple value
$\ttt{x++a}$, the federation can publicly open the value since it is
masked by the random value. This is expressed using the coercion
$\ttt{as RECON(x) +  r[x++a]@3}$.

>>>>

We add coercions and typing assertions to the $\ttt{secopen}$ function
to specify properties of secure openings. After noninteractively
summing a wire value $\ttt{x}$ and a random Beaver triple value
$\ttt{x++a}$, the federation can publicly open the value since it is
masked by the random value. This is expressed using the coercion
$\ttt{as RECON(x) +  r[x++a]@3}$. The coercion then allows the
opened value to be declared $\ttt{public}$.

In the \ttt{mult} function, each client $\ttt{i}$ symmetrically
computes:
$$
\ttt{((m[z++"d"] * m[y]) + (-m[z++"e"] * m[z++"a"]) + m[z++"c"])@i}
$$
Since $\ttt{m[z++"d"]@i : public}$ and $\ttt{m[z++"e"]@i : public}$
are both established by $\ttt{secopen}$, and
$\ttt{m[y]@i}$, $\ttt{m[z++"a"]@i}$, and $\ttt{m[z++"c"]@i}$ are
all declared to be shares in preconditions, we have that each
of $\ttt{m[z++"d"] * m[y]@i}$ and $\ttt{-m[z++"e"] * m[z++"a"]}$
are shares, so the gate outputs are shares, and this will
be successfully checked by syntax-directed $\Vdash$ type checking that
results from the declaration $\ttt{[m[z]@i1,m[z]@i2] : shares}$.
